Appendix0\_10

### 2018-08-17 paper/Appendices/AppendixD.tex
appendix C figlevel 1 CW4

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Appendix0\_10},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{255,255,255}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.67,0.33,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.57,0.30,0.62}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.24,0.68,0.91}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{1.00,0.33,0.00}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.54,0.53,0.53}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.38,0.47,0.50}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.79,0.38,0.79}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.39,0.29,0.61}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.58,1.00}{\textbf{#1}}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.00,0.43,0.16}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.34,0.68}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.69,0.50,0.00}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{#1}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\textbf{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.75,0.01,0.01}{\underline{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.12,0.11,0.11}{#1}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Appendix0\_10}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\begin{document}
\maketitle

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}

\CommentTok{# Change the data path accordingly ----------------------------------------}

\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}

\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}

\CommentTok{# Read the data into memory -----------------------------------------------}

\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}

\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the variables needed -------------------------------------------}

\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
                 \DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}

\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age}\OperatorTok{>=}\DecValTok{19}\NormalTok{,] }\CommentTok{# keep participants who aged 19 or older}
\KeywordTok{rm}\NormalTok{(data, data56, data78) }\CommentTok{# remove the unneeded big dataset}

\NormalTok{dfs2}

\CommentTok{# Calculate the time (minute and hour) when they eat ----------------------}

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr,}\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
                                                              \OtherTok{TRUE}\NormalTok{)]}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
                                             \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
                                            \StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60}\OperatorTok{*}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN)}\OperatorTok{+}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id,dfs2}\OperatorTok{$}\NormalTok{DayNo,dfs2}\OperatorTok{$}\NormalTok{MealMinN0),]}

\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id)) ## number of participants = 6155}

\CommentTok{# Create a subset data with only the first observation of each participant --------}

\NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# #SurveyYear : 
#             Frequency Percent Cum. percent
# NDNS Year 1       801   13.01        13.01
# NDNS Year 2       812   13.19        26.21
# NDNS Year 3       782   12.71        38.91
# NDNS Year 4      1055   17.14        56.05
# NDNS Year 5       625   10.15        66.21
# NDNS Year 6       663   10.77        76.98
# NDNS Year 7       703   11.42        88.40
# NDNS Year 8       714   11.60       100.00
#   Total          6155  100.00       100.00
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# how many men and women --------------------------------------------------}

\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(Sex, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# Sex : 
#          Frequency Percent Cum. percent
# 1            2537   41.22        41.22 Men
# 2            3618   58.78       100.00 Women
#   Total      6155  100.00       100.00
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# create a variable combine id and day No ---------------------------------}

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# eating time can be calculated --------}

\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek),  }
\NormalTok{                summarise, }\DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg), }
                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Englystfibreg),}
                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Fatg), }
                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Proteing), }
                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Alcoholg), }
                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Nonmilkextrinsicsugarsg))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 6.429822 min}

\CommentTok{# reset the time intervals into time slots --------------------------------}

\NormalTok{### Breakfast:       6am to 9am}
\NormalTok{### morning snack:   9am to 12noon}
\NormalTok{### lunch:           12noon to 2pm}
\NormalTok{### afternoon snack: 2pm to 5pm}
\NormalTok{### dinner:          5pm to 8pm}
\NormalTok{### night snack:     8pm to 10pm}
\NormalTok{### midnight:        10pm to 6am}

\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
                        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}

\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}

\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}

\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}

\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# time slot can be calculated --------}
\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
\NormalTok{                summarise, }
                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
                \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
                \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
                \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
                \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
                \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.74195 mins }

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}

\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}

\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
\CommentTok{# with 0 energy intake }
\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}

\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}

\NormalTok{vecid<-}\KeywordTok{unique}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{id)}

\CommentTok{# Filter the data by observation day--------------------------------------------}

\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
           \StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
                                       \StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
                                       \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{vecid1<-}\KeywordTok{unique}\NormalTok{(dta_day1}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
\NormalTok{vecid2<-}\KeywordTok{unique}\NormalTok{(dta_day2}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6153}
\NormalTok{vecid3<-}\KeywordTok{unique}\NormalTok{(dta_day3}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6151}
\NormalTok{vecid4<-}\KeywordTok{unique}\NormalTok{(dta_day4}\OperatorTok{$}\NormalTok{id) }\CommentTok{# n = 6026}

\NormalTok{Noday1 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid1) }\CommentTok{# two subjects did not have day 1 data}

\NormalTok{Noday2 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid2) }\CommentTok{# two subjects did not have day 2 data }

\NormalTok{Noday3 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid3) }\CommentTok{# four subjects did not have day 3 data }

\NormalTok{Noday4 <-}\StringTok{ }\KeywordTok{setdiff}\NormalTok{(vecid, vecid4) }\CommentTok{# 129 subjects did not have day 4 data}

\CommentTok{# Long to wide data -------------------------------------------------------}

\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ Carbo)}

\KeywordTok{head}\NormalTok{(dta_d1_wide)}
\KeywordTok{names}\NormalTok{(dta_d1_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(dta_d1_wide)}

\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ Carbo)}

\KeywordTok{head}\NormalTok{(dta_d2_wide)}
\KeywordTok{names}\NormalTok{(dta_d2_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(dta_d2_wide)}

\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ Carbo)}

\KeywordTok{head}\NormalTok{(dta_d3_wide)}
\KeywordTok{names}\NormalTok{(dta_d3_wide)[}\DecValTok{6}\OperatorTok{:}\DecValTok{12}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"H6_9"}\NormalTok{, }\StringTok{"H9_12"}\NormalTok{, }\StringTok{"H12_14"}\NormalTok{, }\StringTok{"H14_17"}\NormalTok{, }
                              \StringTok{"H17_20"}\NormalTok{, }\StringTok{"H20_22"}\NormalTok{, }\StringTok{"H22_6"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(dta_d3_wide)}

>>>>

% Appendix Template

\chapter{R \& Stata codes for processing individual level data analysis} % Main appendix title

\label{AppendixD}
\linespread{0.8}
